\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-13 manuscript.tex
* Modification figure-captions

\caption{Development of LEBA}\label{fig:FlowchartFig}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCor-1}

@@

{\centering \includegraphics[width=1\linewidth,height=2\textheight]{manuscript_files/figure-latex/facIdFig-1}

@@

{\centering \includegraphics[width=1\linewidth,height=0.5\textheight]{Manuscript.figures/EFAplot}

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}). Table\ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. However, the histogram of the absolute values of non-redundant residual-correlations Fig\ref{fig:EFAResiduals} showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring. (Desjardins \& Bulut, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\ref{tab:sixFacTab}).

Internal consistency reliability coefficient Cronbach's alpha assumes that all the factor- loading of the items under a factor are equal (Graham, 2006; Novick \& Lewis, 1967) which is not the case in our sample. Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature (Gadermann, Guhn, \& Zumbo, 2012; Zumbo, Gadermann, \& Zeisser, 2007). Subsequently to get better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous. Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability. In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .94. All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained 9.93\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .76. Items under this factor commonly investigate an individual's hours spent outdoor. The third factor contained five items and explained 8.83\% of the total variance. Items under this factor dealt with the specific behaviors pertaining to sleep. The internal consistency reliability coefficient was, ordinal \(\alpha\) = .75. The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, ordinal \(\alpha\) = .72. These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time. Lastly, the fifth factor contained six items and explained 6.14\% of the total variance. This factor tried to measure an individual's behavior lead by the awareness of light's influence on health. The internal consistency reliability was, ordinal \(\alpha\) = .62 . It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.

@@

\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResiduals}
\end{figure}

\begin{figure}
\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ }\label{fig:gtPic}
\end{figure}

@@

We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(Desjardins \& Bulut, 2018). Several indices are suggested to measure model fit. These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015). Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit. Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the \(\chi^2\) test. However, the \(\chi^2\) test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015). Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y. Yu, 2002). Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA. Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = .12). Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).

Internal consistency ordinal \(\alpha\) for the five factors of LEBA were .96, .83, .70, .69, .52 respectively. We also estimated the internal consistency reliability of the total scale using Mcdonald's omega(total) coefficient which is a better reliability estimate for multidimensional constructs(Dunn, Baguley, \& Brunsden, 2014; Sijtsma, 2009). McDonald's omega(total) coefficient for the total scale was .73.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figcfa-1} \caption{(A) Five Factor Model of LEBA}\label{fig:figcfa}
\end{figure}

\hypertarget{measurement-invariance}{%
\section{Measurement Invariance}\label{measurement-invariance}}

Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016). We used a structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}. Our measurement invariance testing involved establishing configural, metric, scalar, and residual invariance (Widaman \& Reise, 1997). MI models are nested type models of which configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model, along with the assumption of the configural model, assumes that factor-loadings of the items across the two groups will be equal, indicating each item contributes to the measured construct equivalently for both groups. Along with these assumptions, scalar invariance assumes that item intercepts to be equivalent across groups. The scalar invariance model indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model holds all the mentioned assumptions as true and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999). We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.-Y. Yu, 2002). Table \ref{tab:InvarianceTab} summarized the fit indices. The comparison among different measurement invariance models was made using the \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI. If the \(\Delta \chi^2\) test for model fit is not statistically significant (p\textless0.05) (Dimitrov, 2010), the particular invariance model was accepted. We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons. Table \ref{tab:InvarianceTab} indicates that our fitted model had acceptable fit indices for all of the fitted MI models. The model fit does not significantly decrease across the nested models up to the scalar MI model. The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:itmeinfo}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Blue filter (b) Natural light (c) Smart device (d) Sleep environment (E) Electic light}\label{fig:Testinfo}
\end{figure}

Test information curve (TIC) (\ref{fig:Testinfo}) indicate the amount of information an the full-scale carry along the latent trait continuum. As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (\ref{fig:Testinfo}). These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))). Also the amount of information changed rather steadily with the change of (\(\theta\)). Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor. The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.

@@

\caption{\label{tab:itemfittab}}

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:personfit}
\end{figure}

Next, we generated scale characteristics curve (\ref{fig:scalechar}) which plotted estimated theta score against the expected true score. The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:scalechar}
\end{figure}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-tabledown}{}}%
Anwar Siraji, M. (2021). \emph{Tabledown: A companion pack for the book "basic \& advanced psychometrics in r"}. Retrieved from \url{https://github.com/masiraji/tabledown}

\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-RN1272}{}}%
Yu, C.-Y. (2002). \emph{Evaluating cutoff criteria of model fit indices for latent variable models with binary and continuous outcomes} (Thesis). {ProQuest Dissertations Publishing}.

@@

\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}

>>>>

\caption{Development of long and short form of LEBA}\label{fig:FlowchartFig}
\end{figure}

@@

{\centering \includegraphics[width=1\linewidth,height=1.5\textheight]{manuscript_files/figure-latex/figCor-1}

@@

{\centering \includegraphics[width=1\linewidth,height=2.5\textheight]{manuscript_files/figure-latex/facIdFig-1}

@@

{\centering \includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/EFAplot}

@@

With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items. (cross-loading items and poor factor loading (\textless.30) items). Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30. We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}). Table\ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items. The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients. The commonalities ranged between .11 to .99. However, the histogram of the absolute values of non-redundant residual-correlations Fig\ref{fig:EFAResiduals} showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring. (Desjardins \& Bulut, 2018). Subsequently, we fitted a six-factor solution. However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\ref{tab:sixFacTab}).
Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal (Graham, 2006; Novick \& Lewis, 1967) which is not the case in our sample. Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature (Gadermann, Guhn, \& Zumbo, 2012; Zumbo, Gadermann, \& Zeisser, 2007). Subsequently to get better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous (Zumbo et al., 2007). Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability. In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .94. All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained 9.93\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .76. Items under this factor commonly investigated an individual's hours spent outdoor. The third factor contained five items and explained 8.83\% of the total variance. Items under this factor dealt with the specific behaviors pertaining to using phone and smart-watch in bed. The internal consistency reliability coefficient was, ordinal \(\alpha\) = .75. The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, ordinal \(\alpha\) = .72. These five items investigated the behaviors related to individual's light exposure before bedtime. Lastly, the fifth factor contained six items and explained 6.14\% of the total variance. This factor captured individual's morning and daytime light exposure related behavior. The internal consistency reliability was, ordinal \(\alpha\) = .62 . It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.

@@

\caption{ Histogram of residuals:  five-factor solution}\label{fig:EFAResiduals}
\end{figure}

\begin{figure}
\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
\end{figure}

@@

We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature (Desjardins \& Bulut, 2018). Several indices are suggested to measure model fit which can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015). Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR). Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit. Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the \(\chi^2\) test. However, the \(\chi^2\) test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015). Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C. Yu, 2002). We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA. Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = .12). Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
Internal consistency ordinal \(\alpha\) for the five factors of LEBA were .96, .83, .70, .69, .52 respectively. We also estimated the internal consistency reliability of the total scale using Mcdonald's \(\omega\) (total) coefficient which is a better reliability estimate for multidimensional constructs (Dunn, Baguley, \& Brunsden, 2014; Sijtsma, 2009). McDonald's omega(total) coefficient for the total scale was .73.

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.5\textheight]{manuscript_files/figure-latex/figcfa-1} \caption{Five Factor CFA Model of LEBA}\label{fig:figcfa}
\end{figure}

\hypertarget{measurement-invariance}{%
\subsection{Measurement Invariance}\label{measurement-invariance}}

Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016). We used structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}. Our measurement invariance testing involved successively comparing the nested models: configural, metric, scalar, and residual invariance models with each others (Widaman \& Reise, 1997). Among these nested models configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
The invariance model fit of our scale was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999). We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C. Yu, 2002). Table \ref{tab:InvarianceTab} summarized the fit indices. The comparison among different measurement invariance models was made using the \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attained the highest level of the MI. A non-significant \(\Delta \chi^2\) test between two MI models fit indicates mode fit does not significantly decrease for the superior model (Dimitrov, 2010) thus allowing the superior level of invariance model to be accepted. We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons. Table \ref{tab:InvarianceTab} indicates that our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models up to the scalar MI model. The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:itmeinfo}
\end{figure}

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:Testinfo}
\end{figure}

Test information curve (TIC) (Figure \ref{fig:Testinfo}) indicate the amount of information an the full-scale carry along the latent trait continuum. As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (figure \ref{Fig:Testinfo}). These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))). Also the amount of information changed rather steadily with the change of (\(\theta\)). Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor. The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.

@@

\caption{\label{tab:itemfittab}Item fit statistics for the fitted models}

@@

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:personfit}
\end{figure}

Next, we generated scale characteristics curve (Figure \ref{fig:scalechar}) which plotted estimated theta score against the expected true score. The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models ((a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:scalechar}
\end{figure}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-ufs}{}}%
Peters, G.-J. (2021). \emph{Ufs: Quantitative analysis made accessible}. Retrieved from \url{https://CRAN.R-project.org/package=ufs}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-tabledown}{}}%
Siraji, M. A. (2021). \emph{Tabledown: A companion pack for the book "basic \& advanced psychometrics in r"}. Retrieved from \url{https://github.com/masiraji/tabledown}

@@

\leavevmode\vadjust pre{\hypertarget{ref-RN1272}{}}%
Yu, C. (2002). \emph{Evaluating cutoff criteria of model fit indices for latent variable models with binary and continuous outcomes} (Thesis). {ProQuest Dissertations Publishing}.

@@

\begin{TableNotes}[para]
\normalsize{\textit{Note.} Only loading higher than .30 is reported}
\end{TableNotes}
